\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-26 papers/jfp/7-experience.tex
Link in the Shake precision in this paper

We consider the lack of change to suggest that \Shake is based on fundamental principles -- principles we can now name and describe as a consequence of \cite{mokhov2018buildsystems}.

>>>>

We consider the lack of change to suggest that \Shake is based on fundamental principles -- principles we can now name and describe as a consequence of \cite{mokhov2018buildsystems}. There are two main aspects of the original \Shake paper \cite{mitchell2012shake} that are described more clearly in this paper, the first is the rebuilder, which is described as verifying step traces in \S\ref{sec-step-traces}. The second is the power of \Shake tasks (called actions in the original paper. Originally these tasks were described as being equivalent to:

\begin{minted}[xleftmargin=10pt]{haskell}
data Action k v = Finished v
                | Depends v (v -> Action)
\end{minted}

In some sense this is the ``free'' version of the \hs{Task Monad} -- the two types form an isomorphism. Similary, \Make tasks were described as equivalent to

\begin{minted}[xleftmargin=10pt]{haskell}
data Rule k v = Rule {depends :: [k], action :: [v] -> v}
\end{minted}

Once again, this type is isomorphism to \hs{Task Applicative}. By describing these types using \hs{Task} we are able to pinpoint the differences (\hs{Monad} vs \hs{Applicative}) and use existing literature to prove what is and isn't possible.
